\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2018-10-12 document/XSGRB_sample_rev1.tex
Adding ref

The \textit{Neil Gehrels Swift Observatory} ({\it Swift}) satellite
\citep{Gehrels2004, Gehrels2009}, which was launched in 2004, has made it
possible to harvest much of the great potential in using GRBs as probes of the
intergalactic medium, which was already hinted at by results from earlier
missions \citep[e.g.,][]{Paradijs2000, Ricker2004}. With the three on-board
instruments, the Burst Alert Telescope \citep[BAT;][]{Barthelmy2005}, the X-Ray
Telescope \citep[XRT;][]{Burrows2005}, and the UltraViolet and Optical Telescope
\citep[UVOT;][]{Roming2005}, \swift~is an ideal observatory for GRB hunting. A
crucial aspect of the success of the {\it Swift} mission has been the extensive
ground-based follow-up observations of the afterglows and of the host galaxies
of the GRBs, involving a large community of researchers. This fruitful
collaboration has been facilitated by the open data access policy of the {\it
	Swift} mission. The close collaboration between detection facilities and
electromagnetic  follow-up campaigns continue to be immensely rewarding, as
recently highlighted by the simultaneous detection of gravitational waves and
light from the neutron star merger in the shape of GW170817/GRB170817A/AT2017gfo
\citep{2017ApJ...848L..14G, 2017ApJ...848L..15S, 2017ApJ...848L..16S, 2017ApJ...848L..17C, 2017ApJ...848L..18N, 2017ApJ...848L..19C, 2017ApJ...848L..27T, 2017ApJ...850L...1L, 2017Natur.551...64A, 2017Natur.551...67P, 2017Natur.551...71T, 2017Natur.551...75S, 2017Sci...358.1583K, LIGOScientificCollaboration2017a, LIGOScientificCollaboration2017}.

>>>>

The \textit{Neil Gehrels Swift Observatory} ({\it Swift}) satellite
\citep{Gehrels2004, Gehrels2009}, which was launched in 2004, has made it
possible to harvest much of the great potential in using GRBs as probes of the
intergalactic medium, which was already hinted at by results from earlier
missions \citep[e.g.,][]{Paradijs2000, Ricker2004}. With the three on-board
instruments, the Burst Alert Telescope \citep[BAT;][]{Barthelmy2005}, the X-Ray
Telescope \citep[XRT;][]{Burrows2005}, and the UltraViolet and Optical Telescope
\citep[UVOT;][]{Roming2005}, \swift~is an ideal observatory for GRB hunting. A
crucial aspect of the success of the {\it Swift} mission has been the extensive
ground-based follow-up observations of the afterglows and of the host galaxies
of the GRBs, involving a large community of researchers. This fruitful
collaboration has been facilitated by the open data access policy of the {\it
	Swift} mission. The close collaboration between detection facilities and
electromagnetic  follow-up campaigns continue to be immensely rewarding, as
recently highlighted by the simultaneous detection of gravitational waves and
light from the neutron star merger in the shape of GW170817/GRB170817A/AT2017gfo
\citep{2017ApJ...848L..14G, 2017ApJ...848L..15S, 2017ApJ...848L..16S, 2017ApJ...848L..17C, 2017ApJ...848L..18N, 2017ApJ...848L..19C, 2017ApJ...848L..27T, 2017ApJ...850L...1L, 2017Natur.551...64A, 2017Natur.551...67P, 2017Natur.551...71T, 2017Natur.551...75S, 2017Sci...358.1583K, 2017Sci...358.1556C, LIGOScientificCollaboration2017a, LIGOScientificCollaboration2017}.
